---
title: "Notes"
author: "Richard Careaga"
date: 2021-08-18
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/func.R"))
```

# Source data from MySQL

* Database: dlf
* Table: y7
* 125Kx48
* credentials via ~/.my.cnf

# Naming conventions

```{r}
knitr::kable(readr::read_csv(here::here("doc/conventions.csv")))
```


## Get field dictionary from SQL

    knitr::kable(get_fields("y7"))

Saved to csv, and edited manually to add descriptions

```{r}
knitr::kable(readr::read_csv(here::here("doc/codebook.csv")))
```

Collect selected variables for stratification tables, by type

```{r}
#   # tableone::CreateTableOne(colnames(x), strata = y, data = x)
#   contTable = tableone::CreateContTable(vars = contVars, strata = y, data = x)
#   catTable  = tableone::CreateCatTable(vars = catVars, strata = y, data = x)
#   intTable  = tableone::CreateCatTable(vars = intVars, strata = y, data = x)
#   dteTable =  tableone::CreateCatTable(vars = dteVars, strata = y, data = x)
#   return(c(contTable,catTable,intTable,dteTable))
# }
# 
# stratify(d,"dtype") -> o

stratify_dte(query(1),"dtype") -> o


```

## Bring in y7 table subset as d

```{r}
d <- query(1)
```


tableone::CreateTableOne("fico",strata = "ltype", data = d6)

dat <- d6 %>% dplyr::select(ltype, fico)
dat <- dat %>% mutate(ltype = as.factor(ltype))

p1 <- ggplot(dat) +
  aes(x = ltype, y = fico, color = ltype) +
  geom_jitter() +
  theme(legend.position = "none") +
  theme_minimal()

p2 <- ggplot(dat) +
  aes(x = ltype, y = fico, color = ltype) +
  geom_boxplot() +
  theme(legend.position = "none") +
  theme_minimal()

p3 <- ggplot(dat) +
  aes(fico, fill = ltype) +
  geom_dotplot(method = "histodot", binwidth = 1.5) +
  theme(legend.position = "none") +
  theme_minimal()

res_aov <- aov(fico ~ ltype, data = dat)

resids <- data.frame(.resid = res_aov$residuals)

# histogram
p4 <- ggplot(resids, aes(.resid)) +
  geom_histogram(color = "black", fill = "grey") +
  theme_minimal()

p5 <- ggplot(resids, aes(sample = .resid)) +
  stat_qq() +
  stat_qq_line() +
  theme_minimal()

p4 + p5
skewness(resids)
kurtosis(resids)

# resids are not normally distributed (and groups not necessarily
# independent). Large n almost always non-normal. ANOVA assumptions
# not satisfied

shapiro.test(sample(res_aov$residuals,5000))

leveneTest(fico ~ ltype, data = dat)

aggregate(fico ~ ltype,
          data = dat,
          function(x) round(c(mean = mean(x), sd = sd(x)), 2)
)


group_by(dat, ltype) %>%
  summarise(
    mean = mean(fico, na.rm = TRUE),
    sd = sd(fico, na.rm = TRUE)
  )


oneway.test(fico ~ ltype,
            data = dat,
            var.equal = TRUE # assuming equal variances
)

res_aov <- aov(fico ~ ltype,
               data = dat
)

summary(res_aov)


oneway.test(fico ~ ltype,
            data = dat,
            var.equal = FALSE # assuming unequal variances
)

post_test <- glht(res_aov,
                  linfct = mcp(ltype = "Tukey")
)

summary(post_test)

TukeyHSD(res_aov)

plot(TukeyHSD(res_aov))

post_test <- glht(res_aov,
                  linfct = mcp(ltype = "Dunnett")
)

summary(post_test)

par(mar = c(3, 8, 3, 3))
plot(post_test)

[Senate hearings](https://www.govinfo.gov/content/pkg/CHRG-111shrg57319/html/CHRG-111shrg57319.htm)

[Class II-A1 balance](https://www.sec.gov/Archives/edgar/data/0001350315/000127727706000178/finallongbeach_20061.htm)504,957,000
[85 II count and balance](https://www.sec.gov/Archives/edgar/data/0001350315/000127727706000178/finallongbeach_20061.htm) 4,235 $1,402,654,390.49

As of 2007-06-01, pool balance was 1685747345
COD pool balance 2442492000
0.6901752

Down 31% 0.3098248


	


