---
title: "Statification tables"
author: "Richard Careaga"
date: "2021-03-31"
output: html_document
---

<style type="text/css">
  body{
  font-size: 18pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions.R"))

```

# Stratification

## Source data from MySQL

* Database: dlf
* Table: y7
* 125Kx48
* credentials via ~/.my.cnf

# Naming conventions

```{r}
knitr::kable(readr::read_csv(here::here("doc/conventions.csv")))

```


## Get field dictionary from SQL

    kniletr::kable(get_fields("y7"))

Saved to csv, and edited manually to add descriptions

```{r}
knitr::kable(readr::read_csv(here::here("doc/codebook.csv")))
```

## Bring in y7 table subset as d for a single deal, LBMLT 2006-1

```{r}
d <- query(1)
```

## DescTools

```{r}
DescTools::Desc(d$cltv)
DescTools::Desc(d$down)
DescTools::Desc(d$dti)
DescTools::Desc(d$dtype)
DescTools::Desc(d$fico)
DescTools::Desc(d$grade)
DescTools::Desc(d$ltype)
DescTools::Desc(d$margin)
DescTools::Desc(d$nrate)
DescTools::Desc(d$ebal)
DescTools::Desc(d$orate)
DescTools::Desc(d$otype)
DescTools::Desc(d$ptype)







```

## Selected variables

```{r}
# tab1_cat  <- tableone::CreateTableOne(data = d[c(catVars)])
# tab1_cont <- tableone::CreateTableOne(data = d[c(contVars)])
# tab1_int  <- tableone::CreateTableOne(data = d[c(intVars)])
# print(tab1_cat, showAllLevels = TRUE, formatOptions = list(big.mark = ","))
# tab1_cat
# tab1_cont
# tab1_int
```

## Classify and select variables for stratification tables

One-time, with saved result. For use in {tableone}

    codebook <- readr::read_csv(here::here("doc/codebook"))
    var_num  <- "decimal"
    var_cat  <- "varchar"
    var_dte  <- "date"
    var_int  <- "int"
    omit_num <- c("lat","lng","ctapeno","gainloss","liq","remit","sbal","servno","sint","sprin","spymt")
    omit_int <- c("zip","ppp","dptd","dfpd")
    omit_cat <- c("city","deal","issuer")
    omit_dte <- NULL # fix pod/rdate
    contVars <- colnames(d[,stringr::str_detect(codebook$Type,var_num)])
    intVars  <- colnames(d[,stringr::str_detect(codebook$Type,var_int)])
    dteVars  <- colnames(d[,stringr::str_detect(codebook$Type,var_dte)])
    catVars  <- colnames(d[,stringr::str_detect(codebook$Type,var_chr)])
    contVars <- setdiff(contVars,omit_num)
    intVars  <- setdiff(intVars, omit_int)
    dteVars  <- setdiff(dteVars, omit_dte)
    catVars  <- setdiff(catVars,omit_cat)
    VarsList  <- list(contVars = contVars,dteVars = dteVars,intVars = intVars,catVars = catVars)
    saveRDS(VarsList, file = here::here("obj/VarsList.Rds"))

## Tableone stratifications

### Documentation type

```{r}
VarsList <- readRDS(here::here("obj/VarsList.Rds"))

summary(stratify_cont(VarsList,d,"dtype"))
summary(stratify_cat(VarsList,d,"dtype"))
summary(stratify_int(VarsList,d,"dtype"))
#summary(stratify_dte(VarsList,d,"dtype"))
```

### Grade 

```{r}
summary(stratify_cont(VarsList,d,"grade"))
summary(stratify_cat(VarsList,d,"grade"))
summary(stratify_int(VarsList,d,"grade"))
```

### Loan type

```{r}
summary(stratify_cont(VarsList,d,"ltype"))
summary(stratify_cat(VarsList,d,"ltype"))
summary(stratify_int(VarsList,d,"ltype"))
```

### Purpose

```{r}
summary(stratify_cont(VarsList,d,"purpose"))
summary(stratify_cat(VarsList,d,"purpose"))
summary(stratify_int(VarsList,d,"purpose"))
```

### Occupancy type

```{r}
summary(stratify_cont(VarsList,d,"otype"))
summary(stratify_cat(VarsList,d,"otype"))
summary(stratify_int(VarsList,d,"otype"))
```

### Property type

```{r}
summary(stratify_cont(VarsList,d,"ptype"))
summary(stratify_cat(VarsList,d,"ptype"))
summary(stratify_int(VarsList,d,"ptype"))
```
